---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r echo = FALSE}
suppressPackageStartupMessages(library("tidyverse"))
```


### 2020-05-25 

**Assessing the portfolio**

The grading scale is based on the Institute's [grade descriptions](https://www.rose-hulman.edu/campus-life/student-services/registrar/rules-and-procedures/grades.html), summarized as:

- “A” (4.0 points) is an honor grade demonstrating originality or creativity. This level of work requires one to answer the question "Compared to what?" in depth. Often, more data is required for comparisons over time or to other data that suggest alternative cause and effect. 
- “B” (3.0 points) is awarded for thorough competence
- “C” (2.0 points) indicates that minimum standards have been met

The major deliverables and their relative weights are:

- 70% Portfolio of data displays and written critiques, Weighting the 6 essays and the 6 graphs equally, each has a weight of 5.83% =  70% / 12, rounded so the total sum of weights = 70%. 
- 15% Timely written responses to the reading prompts and the presentation prompts. Equally weighting the Reading responses and Presentation notes yields a 7.5% weight for each. 
- 15% Presenting your work and participating in small-group discussions

```{r echo = FALSE}
df <- wrapr::build_frame(
  "weight" , "item"             , "grade"    |
  0.058  , "D1"                  , 3         |
  0.058  , "D1 essay"            , 3         |
  0.058  , "D2"                  , 3         |
  0.058  , "D2 essay"            , 3         |
  0.058  , "D3"                  , 3         |
  0.058  , "D3 essay"            , 3         |
  0.058  , "D4"                  , 3         |
  0.058  , "D4 essay"            , 4         |
  0.059  , "D5"                  , 4         |
  0.059  , "D5 essay"            , 4         |
  0.059  , "D6"                  , 4         |
  0.059  , "D6 essay"            , 3         |
  0.075  , "Presentation notes"  , 2         |
  0.075  , "Reading responses"   , 3         |  
  0.15   , "Presenting and group discussion"   , 4)

df %<>% 
  select(item, weight, grade) %>% 
  mutate(subtotals = round(grade * weight, 2)) %>% 
  mutate(comment = "")

df$comment[df$item == "D4"] <- "Humanizing the fatalities is very well done, though it might have benefited from including crew and spectators as well."

df$comment[df$item == "D4 essay"] <- "A well-developed argument with meaningful consequences."

df$comment[df$item == "D5"] <- "The progression from the original infographic to your map to your dot plot is engaging. "

df$comment[df$item == "D5 essay"] <- "Your discussion of the graphical lie and how and why you revised the graphic is clear, concise, and complete."

df$comment[df$item == "Presentation notes"] <- "Responses are missing for 4 of the 6 Presentation rtesponses. This would earn a grade of 1 point except that I know you took notes during our discussions and followed up on them. "

knitr::kable(df)
```


Your total is `r sum(df$subtotals)` out of a possible total of 4.0. Routinely, this would be a course grade of "B". However, by learning on your own to graph the map in D5, you also satisfied one of the features of the cancelled D7 assignment. That element of original work warrants the next higher grade of "B+". Nicely done. 

It was a pleasure to work with you this term, Gabe. Best of luck!

--Richard Layton





### 2020-05-14

**RL comments** 

- Edited the D5 map design to eliminate the horizontal lines





### 2020-04-15 D2 graph and D1 essay

**RL comments** 

- Try a reorganization of the essay with the story first, including a journalistic-style headline that tells the main story. 
- Then you can have a separate section devoted to discussing the design of the display. You can move the "D1" details that currently start the essay to the design section. 
- Use sentence case for all text in the display. Capitalize the first word, proper nouns, and acronyms only. 
- You can add a caption below the figure that starts, Figure 1. then a descriptive caption. The title above the graph can still be used. 
- In the sign section, use terminology from the Doumont paper to describe the visual story, explain the data structure and how the graph design is appropriate for the structure of the data
- D2 multiway graph not ready, but data is selected. ]







### 2020-04-08 D1 studio

**RL comments**

ACT scores are quantitative, suggests a scatterplot because you said you were interested in a correlation between ACT score and potential earnings

What is the provenance of the data? How many years? What set of colleges? etc. 


**GS** 



### 2020-03-31

**RL** I could not fix the knitr problem with relative file paths. So I have used a workaround. See the work I added to the `0301-markdowen-basics.Rmd` script.  Before knitting the script, install the `magick` package. 

**GS** 
