---
title: "Test Report"
author: "Gabe Severyn"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r echo = FALSE}
library("knitr")  
library("ggplot2")
library("graphclassmate")
opts_knit$set(root.dir = "../")  
opts_chunk$set(echo = FALSE) 

library(dplyr)
```

## Introduction

This display illustrat es the distribution of speeds attained by skiers
in three downhill events in the 2012 Olympic Winter Games disaggregated
by sex.

## Requirements 

This display meets the data requirements for D1 distributions

- 250 observations 
- One quantitative variable (speed) 
- Two categorical variables: sex (2 levels) and event (3 levels)  

This display also meets the following document requirements 

- sports data limit (this display is one of two) 


The following is a glimpse of StarWars characters.
```{r}
data(starwars, package = "dplyr")

glimpse(starwars)


starwars %>% select(films) %>% unlist() %>% unique()
```


Graph of worlds and number of characters all it home.
```{r}
starwars_worlds <- starwars %>% 
    filter(!is.na(homeworld)) %>% 
    select(homeworld) %>% 
    count(homeworld) %>% 
    filter(n > 1) %>% 
    mutate(homeworld = forcats::fct_reorder(homeworld, n))

ggplot(starwars_worlds, aes(x = n, y = homeworld)) +
    geom_point(size = 1.5) +
    labs(x = "Character count (for N > 1)", 
       y = "", 
       title = "Home worlds of Star Wars characters") + 
    scale_x_continuous(breaks = seq(from = 2, to = 10, by = 2)) +
    theme_graphclass()
```

This is the output of a separate R script.
```{r}
source("explore/0204-more-R-basics.R")
```

